
\cvsection{Education}
\cvevent{Master in Statistics (with thesis)}{Université Laval}{Sep 2017 -- Dec 2020}{}
\cvevent{Bachelor in Actuarial Science}{Université Laval}{Sep 2012 -- May 2015}{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Anomaly detection using the encoded representation of variational autoencoders (VAE)}
\begin{itemize}
\item In my master degree thesis, I used the encoded representation of a VAE to detect abnormal images from a dataset. I also did compared this approach with traditionnal anomaly detection methods applied on images.\\ \href{https://github.com/stecaron/deep-stat-thesis/blob/master/rapports/main-memoire.pdf}{Find out more}.
\end{itemize}
\smallskip
\smallskip
\cvproject{Semantic segmentation on hockey broadcasts images}
\begin{itemize}
\item In this team project, we designed and trained a convolutional neural network (CNN) model capable of learning the semantic of hockey broadcast images. We annotated the images using polygons, and then trained a model using the U-Net artchitecture to predict a class (red line, blue line, ice, crowd, etc) for every pixel. We also presented this project at 2019 Ottawa Hockey Analytics Conference poster session. \\ \href{https://github.com/stecaron/glo-7030-projet/blob/master/pancarte/main-pancarte.pdf}{Find out more}.
\end{itemize}
\smallskip
\smallskip
\cvproject{Meetup ML in Insurance}
\begin{itemize}
\item I contributed to the organization of a machine learning meetup and I was also responsible for defining the problematic proposed during the hackathon part of the event. The problem asked was to detect green roofs on buildings satellite pictures.
\end{itemize}
\smallskip
\smallskip
\cvproject{Big Data Cup 2021: Ottawa Hockey Analytics Conference}
\begin{itemize}
\item In this competition, we proposed an analysis on the impact of winning offensive zone faceoffs during a hockey game. We participated in the "Open" category.  \\ \href{https://github.com/dot-layer/bigdatacup-2021/blob/main/report/CaronLeCavalierPerreault-BigDataCup2021.pdf}{Find out more}.
\end{itemize}
\smallskip
\smallskip
\cvproject{\textit{.Layer} blog website}
\begin{itemize}
\item I contributed to the building of the NPO blog website using Hugo framework. I also contributed by writting multiple posts and reviewing others. \\ \href{https://www.dotlayer.org/en/}{Find out more}.
\end{itemize}
\smallskip
\smallskip
