\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue!80!black}
}
\usepackage{fontawesome}


\begin{document}
\name{STÉPHANE CARON}
\tagline{Data Scientist}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%\photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{ste.caron@icloud.com}
  \phone{581 997-5006}
%  \mailaddress{Address, Street, 00000 County}
  \location{Montréal, Canada}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
  \linkedin{\href{https://www.linkedin.com/in/ste-caron/}{linkedin.com/in/ste-caron/}}
  \github{\href{https://github.com/stecaron}{github.com/stecaron}}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Senior data scientist}{Intact Insurance}{June 2019 -- Now}{Montréal, Canada}
\begin{itemize}
\item Worked on different claims use-cases involving the usage of cars accidents photos (damages assessment, total loss determination, etc).
\item Used linear regressions and time series to develop a case reserves model aiming to predict the ultimate value of a claim.
\item Involved in the process of interviewing data science interns.
\end{itemize}

\smallskip

\cvevent{Actuarial analyst}{Intact Insurance}{Mar 2018 - June 2019}{Québec, Canada}
\begin{itemize}
\item Developed a fraud detection model intented to detect suspicious claims reported to the company.
\end{itemize}

\divider

\cvevent{Actuarial analyst}{Promutuel Assurance}{May 2015 - Mar 2018}{Québec, Canada}
\begin{itemize}
	\item Developed several dynamic reports on company performances using R reporting tools such as \texttt{RMarkdown} and \texttt{shiny}.
	\item Created and maintened many data extractions programs.
	\item Worked on the development and integration of the first usage based insurance product in the company.
\end{itemize}

\cvsection{Achievements}
\smallskip
\begin{itemize}
\item Associate of the Casualty Actuarial Society (ACAS)
\item IVADO/MILA Deep Learning School (2018)
\item President of \href{https://www.dotlayer.org/en/about/}{.Layer}, a NPO involved in the data science community in Quebec.
\item Sports Vice-President of the association of students in Actuarial Sciences of Laval University (2 years).
\end{itemize}

\cvsection{TECHNICAL SKILLS}
\smallskip
\begin{itemize}
\item R, Python, Git, LaTeX, SQL, Excel, VBA, SAS
\item Linux, AWS Cloud Computing (beginner), Docker (beginner)
\end{itemize}

\cvsection{PERSONAL SKILLS}
\smallskip
\begin{itemize}
\item Having leadership qualities.
\item Great team player.
\item Ability to initiate a project or solving a problem having no clear direction.
\end{itemize}

\cvsection{Hobbies}
\smallskip
\begin{itemize}
\item Fishing, hunting and hiking.
\item Traveling and discovering new places.
\item Cooking and tasting new food.
\end{itemize}

% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}

%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
% \wheelchart{1.5cm}{0.5cm}{%
%   10/10em/accent!30/Sleeping \& dreaming about work,
%   25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
%   5/13em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
%   20/15em/accent!40/Spending time with family,
%   5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
%   30/9em/accent/Showing Yahoo!\ employees that their work has meaning,
%   5/8em/accent!20/Baking cupcakes
% }

\clearpage

% \cvsection[page2sidebar]{Publications}

\nocite{*}

% \printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faFileTextO}{Journal Articles}}, type=article]

% \divider

% \printbibliography[heading=pubtype,title={\printinfo{\faGroup}{Conference Proceedings}},type=inproceedings]

% %% If the NEXT page doesn't start with a \cvsection but you'd
% %% still like to add a sidebar, then use this command on THIS
% %% page to add it. The optional argument lets you pull up the
% %% sidebar a bit so that it looks aligned with the top of the
% %% main column.
% % \addnextpagesidebar[-1ex]{page3sidebar}


\end{document}

